---
title: "Barplot_Ppor_Host"
author: "Veronica Radice"
date: "21/04/2021"
output: html_document
---

# Barplots of Differentially expressed genes

## Coral host
### *Porites porites*

### Import libraries
```{r}
library(ggplot2)
library(scales)
library(dplyr)
library(plyr)
```

### Resources
https://stackoverflow.com/questions/38268741/geom-bar-ggplot2-stacked-grouped-bar-plot-with-positive-and-negative-values-p


### Set working directory
```{r}
setwd("~/Documents/Rprojects/postdoc\ Rprojects/ODU_postdoc_Rprojects/Paper_Ojo_gene-expression/Porites_porites/host/")
```


###############################################################################

# Effect of Destination: Ojo vs. Control

Absolute number of DEG adjusted p-value < 0.1
```{r}
# import data
de.genes <- readRDS("Ppor_Host_DE_genes_RO_RC_padj.1.rds")

# add group pairwise contrast label
de.genes$group <- 'RO-RC'
de.genes$group <- as.factor(de.genes$group)
dim(de.genes)
```

### Count which genes are Upregulated versus Downregulated
LFC = log2FoldChange
```{r}
de.genes$LFC <- ifelse(de.genes$log2FoldChange>0, 'Up', 'Down')
de.genes$LFC <- as.factor(de.genes$LFC)

summary_DEG <- de.genes %>% dplyr::count(group, LFC)
summary_DEG$LFC <- factor(summary_DEG$LFC, levels = c("Up", "Down"))

summary_DEG[1,3] <- summary_DEG[1,3]*(-1)

summary_DEG
```

# Barplot
```{r}
plot.combo <- ggplot(summary_DEG, aes(x = group, fill = LFC)) + 
  geom_bar(data=subset(summary_DEG, LFC=="Up"), aes(y=n, fill = LFC), stat = "identity", width=0.6) + #, binwidth=0
  geom_bar(data=subset(summary_DEG, LFC=="Down"), aes(y=n, fill = LFC), stat = "identity", width=0.6) + #, binwidth=0
  geom_text(data=subset(summary_DEG, LFC=="Up"), aes(group, n, label = n), position = position_dodge(width=0.9), vjust = -0.5) +
  geom_text(data=subset(summary_DEG, LFC=="Down"), aes(group, n, label = -n), position = position_dodge(width=0.9), vjust = 1.5) +
  scale_fill_manual("LFC", values=c("black", "#56B4E9"), labels=c("Down-regulated", "Up-regulated"), guide=guide_legend(reverse=TRUE)) + #colorblind friendly
  ylab("Differentially expressed genes") +
  xlab("Transplantation") + 
  scale_y_continuous(limits = c(-870, 500), breaks = seq(-800, 400, by = 200)) +
  theme_classic() +
  theme(legend.position = "none", panel.background = element_rect(colour = "black"), axis.text.x = element_text(angle = 45, vjust = 0.5)) #axis.text.x=element_text(vjust=0.5, size=10, face="italic"), #legend.position = "bottom",

plot.combo
```

```{r}
# save plot
ggsave("Ppor_Host_DEG_barplot.pdf", plot = plot.combo,  width = 2.2, height = 4, units = "in", dpi = 1200) 
```


### Session Info
```{r}
sessionInfo()
```
